Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-19 papers/clusters.tex
Typos

% Palomar 5
There are scant abundance measurements reported for Palomar 5, for which
most stars in the cluster in Figure \ref{fig:Pal5} belong. We find a mean
metallicity of [Fe/H]$ = -1.3$ (DWH CHECK), which lies between the only
photometric \citep{Geisler_1997} and spectroscopic \citep{Smith_1985,Smith_2002} abundance
measurements for this cluster.  The anti-correlation in C--N and Na--O abundance
have been seen elsewhere \citep[][, respectively]{Smith_1985,Smith_2002}, although
to our knowledge the Mg--Al anti-correlation has never been shown in this cluster.
Indeed, this work contains the largest number of abundances for Palomar 5,
permitting a thorough search of tidally disrupted members \citep[e.g.,][]{Kuzma_2015} 
that have retained the unique cluster abundance signature .

>>>>

% Palomar 5
There are scant abundance measurements reported for Palomar 5, for which
most stars in the cluster in Figure \ref{fig:Pal5} belong. We find a mean
metallicity of [Fe/H]$ = -1.3$ (DWH CHECK), which lies between the only
photometric \citep{Geisler_1997} and spectroscopic \citep{Smith_1985,Smith_2002} abundance
measurements for this cluster.  The anti-correlation in C--N and Na--O abundance
have been seen elsewhere \citep[][respectively]{Smith_1985,Smith_2002}, although
to our knowledge the Mg--Al anti-correlation has not previously been shown for this cluster.
Indeed, this work contains the largest number of abundances for Palomar 5,
permitting a thorough search of tidally disrupted members \citep[e.g.,][]{Kuzma_2015} 
that have retained the unique cluster abundance signature.
